---
title: "Language Course Enrollments App"
author: "Doris"
date: "2023-03-02"
output: 
  ioslides_presentation: 
    widescreen: yes
always_allow_html: true
---

## Synopsis

<font size="3">This App tracks course enrollments in Languages other than English in US degree-granting postsecondary institutions from 1965 to 2016. 

Two functions in the App:

- Year: Select a year to check the language course enrollments in that year.
- Language: Select a language to check the enrollment trends of that language.    
  
    
  
Try the **[App](https://pvxjz6-chen-doris.shinyapps.io/eduData-App/)** now.    
  
The reproducible documents are in this [Github repo](https://github.com/Doris-QZ/Shiny-App-eduData).</font>


## Data

<font size="3">Data Source: [National Center for Education Statistics](https://nces.ed.gov/programs/digest/d19/tables/dt19_311.70.asp)  
  
Data was pre-processed before working on this App.   
  
Here is the first 10 rows of the final data:  </font>    
  
<center>
```{r, echo=FALSE, message=FALSE, comment=""}
library(tidyverse)
library(shiny)
library(scales)
enrollments <- read.csv("eduData-App/data/enrollments.csv")   
enrollments <- enrollments[,-1]
head(enrollments,10)
```
</center>

## Code of ui.R

```{r}
        shinyUI(fluidPage(
                titlePanel("Language Course Enrollments in US (1965--2016)"),
                sidebarLayout(
                        sidebarPanel(
                                p("This App tracks course enrollments in Languages other than English in US degree-granting 
                                postsecondary institutions from 1965 to 2016. You can select a year to check the language course 
                                   enrollments in that year from 'Enrollments in the Year' tab, or select a language to check the 
                                   enrollment trends of that language in 'Enrollments Trend' tab."),
                                tags$a(href="https://nces.ed.gov/programs/digest/d19/tables/dt19_311.70.asp", 
                                       "Data Source: National Center for Education Statistics", target="_blank"),
                                br(),
                                selectInput(inputId="year", label=strong("Year"),
                                            choices=unique(enrollments$year), selected="1965"),
                                h6("* Select a year to check the language courses enrollments in that year."), 
                                selectInput(inputId="language", label=strong("Language Course"), 
                                            choices=unique(enrollments$language), selected="Chinese"),
                                h6("* Select a language to check the enrollment trends of that language."),
                                h6("* Greek means Ancient Greek."),
                                h6("* Chinese includes Cantonese and Mandarin.")),
                        mainPanel(
                                tabsetPanel(type="tabs",
                                            tabPanel("Enrollments in the Year", br(), textOutput("year"),
                                                     plotOutput("barplot")),
                                            tabPanel("Enrollments Trend", br(), textOutput("language"), 
                                                     plotOutput("trendplot")))))))
```

## Code of server.R
```{r}
        shinyServer(
                function(input, output, session){
                        output$year <- renderText({paste("Enrollments in the year", input$year)})
                        output$barplot <- renderPlot({
                           year_data <- reactive({
                               enrollments %>% 
                                     filter(year == input$year & language != "All" & language != "Other languages") %>% 
                                     mutate(language=ifelse(language=="American Sign Language", "ASL", language)) })
                           percents <- reactive({percent(year_data()$enrollment/sum(year_data()$enrollment), accuracy=0.01)})
                           ggplot(data=year_data(), aes(x=reorder(language, -enrollment), y=enrollment))+
                                        geom_bar(stat="identity", fill="salmon", col="white")+
                                        labs(x="Language", y="Enrollments", caption="* ASL: American Sign Language")+
                                        coord_cartesian(ylim=c(0,880000))+
                                        scale_y_continuous(labels = comma)+
                                        geom_label(aes(label=enrollment), vjust=-0.3)+
                                        geom_text(aes(label=percents()), vjust=1.2, size=4, col="white")+
                                        theme(plot.caption = element_text(hjust = 0, size=12))})
                        output$language <- renderText({paste("Enrollments Trend of", input$language)})
                        output$trendplot <- renderPlot({
                                lang_data <- reactive({enrollments[enrollments$language == input$language,]})
                                ggplot(data = lang_data(), aes(x=factor(year), y=enrollment))+
                                        geom_bar(stat="identity", fill="lightgreen")+
                                        labs(x="Year", y="Enrollments")+
                                        geom_label(aes(label=enrollment), vjust=1.5)})})

```
<font size="3">* Code is simplified a bit for fitting in this slide.<font>
